Stay in shape! Homework exam II

### 2016-03-18 geometricAlgorithms/homeworkExam/2/homeworkExam.tex
after meeting suggestions

\documentclass{article}
\usepackage{amsmath}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{pst-solides3d}
\usepackage{auto-pst-pdf}
\usepackage{tikz}
\usepackage{enumerate}
\renewcommand{\thesubsection}{\thesection.\alph{subsection}}
\begin{document}
\author{Jappie Klooster}
\title{Stay in shape! Homework exam II}
\maketitle
\section{A disk and some half-planes}
\subsection{Per case, what can you say about $H$}
\begin{enumerate}[i]
	\item \emph{There is no disk that has its centor non the $x$ axis
			that lies inside all half-planes.}

		There exists some half plan whose's area never crosses the x axis
		(so is either completly above or below y=0).
	\item \emph{There are arbitrarly large disk with the specifications.}

		The half planes do not enclose the disk area.
	\item \emph{The largest disk exists and is unique.}

	\item \emph{There are several equally large largest disks}
\end{enumerate}
\subsection{Deal with case ii in linear worstcase time}
\subsection{Formulate and proof the RIC lemma}
\subsection{Give the RIC algorithm}
\subsection{Prove the expected running time}
% Don't forget to remove constants
\subsection{Eplain why you can't use RIC for points}
\section{A datastructure for horizontal line segments}
\subsection{Analyze the storage requirements}
\subsection{Argue that all horizontal line segs are found}
\subsection{Give psuedo code for the query algorithm}
\subsection{Analyze the query time}
\section{Voronoi nearest neigbour\emph{s}}
%TODO: wtf? maybe with higher order voronoi?? But it won't be log n
\end{document}

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{pst-solides3d}
\usepackage{auto-pst-pdf}
\usepackage{tikz}
\usepackage{enumerate}
\renewcommand{\thesubsection}{\thesection.\alph{subsection}}
\begin{document}
\author{Jappie Klooster}
\title{Stay in shape! Homework exam II}
\maketitle
\section{A disk and some half-planes}
\subsection{Per case, what can you say about $H$}
Let $H_{int}$ be the intersection of halfplanes of $H$.
\begin{enumerate}[i]
	\item \emph{There is no disk that has its centor non the $x$ axis
			that lies inside all half-planes.}

		$H_{int}$ never crosses the x axis,
		so it exists entirely above or below $y=0$. Or the intersection is empty.

	\item \emph{There are arbitrarly large disk with the specifications.}

		$H_{int}$ has no parallel line  to te x axis and
		at most one line crossing the x axis.

	\item \emph{The largest disk exists and is unique.}

		$H_{int}$ crosses the x-axis at least 2 times and
		if there is a line parallel to the x axis then both x-axis crossing
		to be in range of the diameter of the disk.

	\item \emph{There are several equally large largest disks}

		$H_{int}$ produces an area with lines parallel to the x-axis.

\end{enumerate}

\newpage
\subsection{Deal with case ii in linear worstcase time}
\begin{algorithmic}[1]
	\Function{hasArbitrarlylargeDisc}{$H$}
		\State
		$b_r, b_l \gets None$
		\For{$i \gets 1$ to $n$ with $h_i \in H$}

			\If{$h_i$ is parallel to the x-axis}
				\State
				\Return $False$
			\EndIf
			\State
			\Comment{Check where the x axes crossings are, and write it into
			a variable pair, if both pairs are filled its not case ii.}
			\If{$h_i$ points left}
			\State
				$b_r \gets h_i$
			\EndIf
			\If{$h_i$ points right}
			\State
				$b_l \gets h_i$
			\EndIf
			\If{$b_r$ not equal to $None$ and $b_l$ not equal to $None$}
				\State
				\Return $False$
			\EndIf
		\EndFor
		\State
		\Return $True$
	\EndFunction
	\State 
	\State 
\end{algorithmic}
\subsection{Formulate and proof the RIC lemma}
%TODO: een beeetje overtypen van 4.5
Let $1 \leq i \leq n$, and let $c_i$ be the

\subsection{Give the RIC algorithm}

\subsection{Prove the expected running time}
% Don't forget to remove constants
\subsection{Eplain why you can't use RIC for points}
\section{A datastructure for horizontal line segments}

\subsection{Analyze the storage requirements}
%TODO: warning: this is x and y descisions.
\subsection{Argue that all horizontal line segs are found}
\subsection{Give psuedo code for the query algorithm}
%TODO: sla lijnen op geen punten.

\subsection{Analyze the query time}

\section{Voronoi nearest neigbour\emph{s}}
%TODO: wtf? maybe with higher order voronoi?? But it won't be log n
%TODO: we hebben ook bogen. Kun je representateren als een lijn en een punt.
\end{document}
